TBD

### 2021-03-05 outputs/paper/paper.Rmd
post_favor_Sanders by treat

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)

@@

### education level distribution by PID 
```{r educationPID, fig.cap = "Educational level by PID",echo=FALSE, fig.width=10, fig.height=7}
edu <- 
  EDA%>%
  ggplot(aes(x = EDA$educ,fill=EDA$PID, )) +
  geom_bar(position="dodge") +
  labs(title = "Citizens with a high school degree or above are more likely to suppprt democratic and republican party",x= "Educational Level", y="Count")+
  scale_fill_manual(name = "Political Parties",values = c("#DB7558", "#FFCF57","#8FCDD4"))

@@

## post favor by treat
```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Sanders)

ggplot(EDA, aes(x = post_favor_Sanders,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different situations")+
  theme_minimal()

@@

ggplot(aes(x=treat,y=Average_mark),data=post_S)+
  geom_bar(stat="identity",fill=c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  ggtitle("Distribution of feelings towards Sanders in six different situations")+
  xlab("Feelings towards Sanders")

```
# Average deception level by treat
```{r table1,tab.cap="Average deception level of each media format", echo = FALSE}
EDA%>%
  group_by(treat)%>%
  filter(treat != "control")%>%
  summarise("Average Deception Level"=mean(believed_true,na.rm = T))%>%
  knitr::kable(caption = "Average deception level of each media format")

```
=======
### post favor by treat
>>>>>>> 0d76115c88f7b80d6fef4e0a358a9f0f2186dedd

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(kableExtra)
```

@@

### education level distribution by PID 
```{r educationPID, fig.cap = "Educational level by PID",echo=FALSE, fig.width=10, fig.height=7}
edu <- 
  EDA%>%
  ggplot(aes(x = educ,fill=PID, )) +
  geom_bar(position="dodge") +
  labs(title = "Citizens with a high school degree or above are more likely to suppprt democratic and republican party",x= "Educational Level", y="Count")+
  scale_fill_manual(name = "Political Parties",values = c("#DB7558", "#FFCF57","#8FCDD4"))

@@

### post favor by treat
```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Sanders)

ggplot(EDA, aes(x = post_favor_Sanders,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()

@@

ggplot(aes(x=treat,y=Average_mark),data=post_S)+
  geom_bar(stat="identity",fill=c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  xlab("Feelings towards Sanders")

```
### Average deception level by treat
```{r table1,tab.cap="Average deception level of each media format", echo = FALSE,warning=FALSE}
EDA%>%
  group_by(treat)%>%
  filter(treat != "control")%>%
  summarise("Average Deception Level"=mean(believed_true,na.rm = T))%>%
  knitr::kable(caption = "Average deception level of each media format")
```
